---
title: "Data Arrangement for Dependency Models"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description of the Code

Data is manipulated through the R packages to make it compatible with the script used in MATLAB.
For that reason, we grouped N (retrieval trials) by M (number of events). Values indicated binary values (1 or 0). 1 indicates that the respondent has correct trial whereas 0 indicates that respondent has incorrect response.

### Input

As an input, we used raw xlsx file taken from E-prime.
Raw data contains full information of a session. We deducted it to two parameters (event_number, retrieval_trials).

```{r}
library(tidyr)
install.packages("stringr")
library("stringr")
install.packages("tidyverse")
library(splitstackshape)
library(dplyr)
library("writexl") 
install.packages("writexl")
```

## Cleaned Data

A1 is an exported data frame used as a raw data.

``` {r}
attach(A1)
AA <- A1
AA <- AA[,-c(1:44, 46:53, 55:60)] #remove unnecessary columns
AA <- AA[-c(1:43),]  #remove unnecessary rows
names(AA)[names(AA) == "...45"] <- "eventtrial" #rename the variable name
names(AA)[names(AA) == "...54"] <- "acc"  #rename the variable names
BB <- cSplit(AA, "eventtrial", '_') #split the column and remove unnecessary elements
BB <- cSplit(BB, "eventtrial_4", ".jpg") #split the column and remove unnecessary elements
CC <- cbind(BB, AA) #merge the two data frame
CC <- CC[,-c(1,2,4,6)] #remove the replicated columns
View(CC)
new_df<- CC %>% spread(key = eventtrial_2, value = acc)  #transform the matrix
names(new_df)[names(new_df) == "eventtrial_4_1"] <- "event_number" #rename the variable name
View(new_df)
write_xlsx(new_df, "/Users/neslihanonay/Desktop/Ulrike_internship/subj01.xlsx")  #save the data frame to the computer. Change path file in the case of need to update. Also, change subj01 to subj02, subj03, etc... for each participant
```

For each participant, code should be run. The output can be used to directly apply to model in MATLAB. There needs to be rename the raw file as "A1" OR there needs to be renaming A1 with a raw data file in above code.




